%-------------------------
% Callum Stein Cover Letter in Latex
% Author : Callum Stein
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\input{glyphtounicode}

% Helvetica (match resume)
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins (same as resume)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedright
\raggedbottom

\pdfgentounicode=1

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c}
\begin{tabular}[c]{c}
\textbf{\Huge \scshape Callum Stein} \\
\end{tabular} &
\begin{tabular}[c]{r}
\small 0422 923 084 $|$ \href{mailto:callumstein.1@gmail.com}{callumstein.1@gmail.com} \\
\small \href{https://www.linkedin.com/in/callum-stein}{linkedin.com/in/callum-stein} $|$ 
\href{https://github.com/CallumStein}{github.com/CallumStein}
\end{tabular}
\end{tabular*}

\vspace{12pt}

%----------DATE----------
\small \today

\vspace{12pt}

%----------EMPLOYER DETAILS----------
\small
Hiring Manager \\
Company Name \\
City, State \\

\vspace{12pt}

%----------GREETING----------
Dear Hiring Manager,

\vspace{10pt}

%----------OPENING----------
I am writing to express my interest in the Software Engineer position at Company Name. With experience across both full-stack development and data engineering, I have contributed to building and delivering scalable, high-impact systems within enterprise environments.

\vspace{10pt}

%----------BODY PARAGRAPH 1----------
In my current role at DXC Technology, I have worked on large-scale data transformation initiatives, engineering and maintaining ETL workflows that process millions of records within critical delivery windows. This experience has strengthened my ability to design reliable, high-performance systems while collaborating closely with stakeholders to translate business requirements into technical solutions.

\vspace{10pt}

%----------BODY PARAGRAPH 2----------
Previously, as a Full-Stack Engineer, I contributed to the development of a modern web platform supporting over 400,000 users. I built scalable frontend applications using React, TypeScript, and Next.js, alongside ASP.NET microservices deployed via Docker. I also implemented unit testing practices using Jest, improving code quality and system reliability within a CI/CD-driven environment.

\vspace{10pt}

%----------BODY PARAGRAPH 3----------
I thrive in Agile environments where I can actively contribute technical insights, collaborate with cross-functional teams, and continuously improve system performance and delivery processes. I am particularly motivated by opportunities to build scalable systems and deliver meaningful impact through well-engineered solutions.

\vspace{10pt}

%----------CLOSING----------
I would welcome the opportunity to contribute my skills and experience to your team. Thank you for your time and consideration.

\vspace{10pt}

Sincerely, \\
Callum Stein

\end{document}