%-------------------------
% Callum Stein Resume in Latex
% Author : Callum Stein
% Based off of: https://github.com/jakegut/resume/blob/master/resume.tex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% Helvetica (Arial-like)
 \usepackage[scaled]{helvet}
 \renewcommand{\familydefault}{\sfdefault}


\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{6pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c}
\begin{tabular}[c]{c}
\textbf{\Huge \scshape Callum Stein} \\
\end{tabular} &
\begin{tabular}[c]{r}
\small 0422 923 084 $|$ \href{mailto:callumstein.1@gmail.com}{callumstein.1@gmail.com} \\
\small \href{https://www.linkedin.com/in/callum-stein}{linkedin.com/in/callum-stein} $|$ 
\href{https://github.com/CallumStein}{github.com/CallumStein}
\end{tabular}
\end{tabular*}
\vspace{-6pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{
\textbf{Languages:} C\#, POSIX/BASH Script, SQL (SQL Server, Oracle), Python, Typescript, HTML/CSS \\
\textbf{Technologies:} Linux, ASP.NET, React, Next.js, Azure, Informatica IICS \\
\textbf{Developer Tools:} Git, Informatica Data Quality, Azure Data Factory, Azure DevOps, VS Code 
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Data Engineer}{Feb. 2025 -- Present}
  {DXC Technology}{Sydney, Australia}
  \resumeItemListStart
    \resumeItem{Architected, developed, and maintained large-scale ETL integrations using \textbf{Informatica IICS}, \textbf{SQL Server stored procedures}, and \textbf{UNIX shell scripting}, processing 5M+ customer records across 50+ workflows.}
    \resumeItem{Engineered and optimised ETL data workflows for high-volume processing (15M+ records per cycle), applying \textbf{modern data platform and warehousing principles} (Data modelling, Metadata Management, Scalable design approach).}
    \resumeItem{Enhanced system performance and reliability through proactive optimisation, debugging, and query tuning, ensuring stable execution in time-critical migration windows.}
    \resumeItem{Partnered with business stakeholders and cross-functional teams to investigate incidents, perform root cause analysis, and translate complex requirements into actionable technical solutions.}
    \resumeItem{Contributed as a technical voice within \textbf{Agile/Scrum delivery cycles}, participating in sprint planning and stakeholder showcases while supporting CI/CD deployment processes for reliable, repeatable releases.}
\resumeItemListEnd

\resumeSubheading
  {Full-Stack Engineer}{Jun. 2024 -- Jan. 2025}
  {DXC Technology}{Sydney, Australia}
  \resumeItemListStart
    \resumeItem{Delivered a cloud-based Novated Leasing and vehicle quoting platform supporting 400,000+ employees, integrating 4 backend microservice APIs to unify employee, vehicle, and quote data.}
    \resumeItem{Developed and optimized frontend components using \textbf{React}, \textbf{TypeScript}, and \textbf{Next.js}, alongside \textbf{ASP.NET} microservice APIs in \textbf{C\#} with \textbf{Docker}, ensuring seamless system integration.}
    \resumeItem{Maintained and supported cloud infrastructure and application services in \textbf{Microsoft Azure}, implementing data pipeline orchistration through \textbf{Azure Data Factory}.}
    \resumeItem{Managed source control, build pipelines, and release processes using \textbf{Azure DevOps}, enabling reliable CI/CD deployments across development, test, and production environments.}
    \resumeItem{Executed CI/CD deployments, resolved production issues, and showcased system updates and live demos to stakeholders, maintaining 99.9\% uptime during release cycles.}
\resumeItemListEnd

\resumeSubheading
  {Assistant Language Teacher}{Aug. 2016 -- Jul. 2021}
  {Saga Board of Education}{Saga-Ken, Japan}
  \resumeItemListStart
    \resumeItem{Led and coordinated English Conversation Education across 3 regional high schools for over 1,000 students, delivering lessons that improved students' speaking and comprehension skills.}
    \resumeItem{Assisted in the management of students reports and grades within the English Education Department.}
    \resumeItem{Planned and managed annual volunteer community events with 20+ participants from the local community, liaising with local businesses and staff to facilitate successful events.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Monash University}{Melbourne, VIC}
    {Master of Information Technology}{Oct. 2021 -- Jul. 2023}
  \resumeSubheading
    {Central Queensland University}{Rockhampton, QLD}
    {Bachelor of Electrical Engineering, First-Class Honours}{Mar. 2011 -- Aug. 2015}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

 \resumeProjectHeading
    {\textbf{LoveYourArea - Sustainable Communities} $|$ \emph{JavaScript, Django, Python, MySQL}}{Jan. 2023 -- May 2023}
    \resumeItemListStart
      \resumeItem{Developed a Django/Python web application utlizing Victorian government public roads and parks data to help Greater Melbourne residents discover local activities and community events.}
      \resumeItem{Implemented backend services with Django/Python and MySQL for event and user management.} 
      \resumeItem{Designed a dynamic, user-friendly frontend in JavaScript to provide tailored community recommendations and seamlessly generate unique walking trail experiences for users.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}